### 2023-01-31 manuscript.tex
Merge branch 'main' of github.com:stain/2022-fdo-paper into main [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/484ae8b4b9e9611eeeb1e0e67f96d5b8bd8b70a4.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/484ae8b4b9e9611eeeb1e0e67f96d5b8bd8b70a4/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4054549790

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/77065153bd22894490553066987dc5130d835eea/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/77065153bd22894490553066987dc5130d835eea}{stain/2022-fdo-paper@7706515}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/484ae8b4b9e9611eeeb1e0e67f96d5b8bd8b70a4/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/484ae8b4b9e9611eeeb1e0e67f96d5b8bd8b70a4}{stain/2022-fdo-paper@484ae8b}
on January 31, 2023.
